ISSP Chile 1999, 2009 & 2019 - Salary Gap & meritocracy

### 2019-09-03 files/20190622_ISSP1999_2009_2019-Chilejuitsa.Rmd
update4sept

```{r }
{
  library(dplyr)
  library(here)
  library(sjlabelled)
  library(sjPlot)
  library(ggplot2)
  library(knitr)
  library(kableExtra)
  library(GPArotation)
  library(lavaan)
  library(semPlot)
  library(Cairo);options(shiny.usecairo=TRUE) # Para la calidad de los plots
}
```

@@

```{r Tabla: CFA, results='asis'}
semTable::semTable(fit1, columns = c("estse", "p"),
                     fits = c("chisq","cfi", "rmsea"),type = "html") 
```

@@

```{r}
file.remove(here("index.html"))
file.copy(from = here("files","20190622_ISSP1999_2009_2019-Chilejuitsa.html"),
          to   = here("index.html"))
```

>>>>

```{r }
{
  library(dplyr)
  library(here)
  library(sjlabelled)
  library(sjPlot)
  library(ggplot2)
  library(knitr)
  library(kableExtra)
  library(GPArotation)
  library(lavaan)
  library(Cairo);options(shiny.usecairo=TRUE) # Para la calidad de los plots
}
```

@@

@@

```{r render, eval=FALSE, include=FALSE}
rmarkdown::render(input = here("files","20190622_ISSP1999_2009_2019-Chilejuitsa.Rmd"))
```
